Spikes demo

### 2018-09-27 analysis/spikesdemo.Rmd
wflow_publish("spikesdemo.Rmd")

```{r plot-mean-signal-vs-estimates, fig.height=5, fig.width=10}
par(cex.axis = 1)
plot(mu.sp,type = "l",col = "black",lwd = ,xlab = "position",ylab = "",
     ylim = c(-0.05,1),xaxp = c(0,1024,4),yaxp = c(0,1,4))
lines(mu.ti,col = "dodgerblue",lwd = 3)
lines(mu.smash,col = "orangered",lwd = 3)
```

>>>>

```{r plot-mean-signal-vs-estimates, fig.height=5, fig.width=10}
par(cex.axis = 1)
plot(mu.sp,type = "l",col = "black",lwd = 3,xlab = "position",ylab = "",
     ylim = c(-0.05,1),xaxp = c(0,1024,4),yaxp = c(0,1,4))
lines(mu.ti,col = "dodgerblue",lwd = 3)
lines(mu.smash,col = "orangered",lwd = 3)
```
